\documentclass{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage[svgnames]{xcolor}
\definecolor{VRNA}{RGB}{0,103,149}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=VRNA,
    filecolor=magenta,      
    urlcolor=VRNA,
    pdftitle={Individual CLA - ViennaRNA Package}
    }

\urlstyle{same}

\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\pagestyle{fancy}
\fancyhf{}
\rhead{\Large{\textbf{ViennaRNA Package}}}
\lhead{\Large{\textbf{Individual Contributor License Agreement}}}
\lfoot{\href{http://harmonyagreements.org/}{Harmony (HA-CLA-I-ANY) Version 1.0}}
\rfoot{Page \thepage \hspace{1pt} of \pageref*{LastPage}}

\renewcommand{\labelenumi}{\alph{enumi})}

\begin{document}

\noindent
Thank you for your interest in contributing to the \texttt{ViennaRNA Package}
(``We'' or ``Us'').
\\\\
\noindent
This contributor agreement (``Agreement'') documents the rights granted by
contributors to Us. To make this document effective, please sign it and send it
to Us by email, following the instructions at
\url{https://www.tbi.univie.ac.at/RNA/contributing.html}.\\\\
This is a legally binding document, so please read it carefully before agreeing
to it. The Agreement may cover more than one software project managed by Us.


\section{Definitions}
\noindent
``You'' means the individual who Submits a Contribution to Us.
\\
\\
\noindent
``Contribution'' means any work of authorship that is Submitted by You to Us in
which You own or assert ownership of the Copyright. If You do not own the
Copyright in the entire work of authorship, please follow the instructions in
\url{https://www.tbi.univie.ac.at/RNA/contributing.html}.
\\
\\
\noindent
``Copyright'' means all rights protecting works of authorship owned or
controlled by You, including copyright, moral and neighboring rights, as
appropriate, for the full term of their existence including any extensions by
You.
\\
\\
\noindent
``Material'' means the work of authorship which is made available by Us to third
parties. When this Agreement covers more than one software project, the Material
means the work of authorship to which the Contribution was Submitted. After You
Submit the Contribution, it may be included in the Material.
\\
\\
\noindent
``Submit'' means any form of electronic, verbal, or written communication sent
to Us or our representatives, including but not limited to electronic mailing
lists, source code control systems, and issue tracking systems that are managed
by, or on behalf of, Us for the purpose of discussing and improving the
Material, but excluding communication that is conspicuously marked or otherwise
designated in writing by You as ``Not a Contribution.''
\\
\\
\noindent
``Submission Date'' means the date on which You Submit a Contribution to Us.
\\
\\
\noindent
``Effective Date'' means the date You execute this Agreement or the date You
first Submit a Contribution to Us, whichever is earlier.
\\
\\
\noindent
``Media'' means any portion of a Contribution which is not software.

\section{Grant of Rights}

\subsection{Copyright License}

\begin{enumerate}
\item You retain ownership of the Copyright in Your Contribution and have the
same rights to use or license the Contribution which You would have had without
entering into the Agreement.
\item To the maximum extent permitted by the relevant law, You grant to Us a
perpetual, worldwide, non-exclusive, transferable, royalty-free, irrevocable
license under the Copyright covering the Contribution, with the right to
sublicense such rights through multiple tiers of sublicensees, to reproduce,
modify, display, perform and distribute the Contribution as part of the
Material; provided that this license is conditioned upon compliance with
Section 2.3.
\end{enumerate}

\subsection{Patent License}
For patent claims including, without limitation, method, process, and apparatus
claims which You own, control or have the right to grant, now or in the future,
You grant to Us a perpetual, worldwide, non-exclusive, transferable,
royalty-free, irrevocable patent license, with the right to sublicense these
rights to multiple tiers of sublicensees, to make, have made, use, sell, offer
for sale, import and otherwise transfer the Contribution and the Contribution in
combination with the Material (and portions of such combination). This license
is granted only to the extent that the exercise of the licensed rights infringes
such patent claims; and provided that this license is conditioned upon
compliance with Section 2.3.

\subsection{Outbound License}
Based on the grant of rights in Sections 2.1 and 2.2, if We include Your
Contribution in a Material, We may license the Contribution under any license,
including copyleft, permissive, commercial, or proprietary licenses. As a
condition on the exercise of this right, We agree to also license the
Contribution under the terms of the license or licenses which We are using for
the Material on the Submission Date.
\\
\\
In addition, We may use the following licenses for Media in the Contribution:
Creative Commons Attribution 4.0 (CC BY 4.0) (including any right to adopt any
future version of a license if permitted).

\subsection{Moral Rights}
If moral rights apply to the Contribution, to the maximum extent permitted by
law, You waive and agree not to assert such moral rights against Us or our
successors in interest, or any of our licensees, either direct or indirect.

\subsection{Our Rights}
You acknowledge that We are not obligated to use Your Contribution as part of
the Material and may decide to include any Contribution We consider appropriate.

\subsection{Reservation of Rights}
Any rights not expressly assigned or licensed under this section are expressly
reserved by You.


\section{Agreement}

You confirm that:
\begin{enumerate}
\item You have the legal authority to enter into this Agreement.
\item You own the Copyright and patent claims covering the Contribution which
are required to grant the rights under Section 2.
\item The grant of rights under Section 2 does not violate any grant of rights
which You have made to third parties, including Your employer. If You are an
employee, You have had Your employer approve this Agreement or sign the Entity
version of this document. If You are less than eighteen years old, please have
Your parents or guardian sign the Agreement.
\item You have followed the instructions in
\url{https://www.tbi.univie.ac.at/RNA/contributing.html}, if You do not own the
Copyright in the entire work of authorship Submitted.
\end{enumerate}


\section{Disclaimer}

EXCEPT FOR THE EXPRESS WARRANTIES IN SECTION 3, THE CONTRIBUTION IS
PROVIDED ``AS IS''. MORE PARTICULARLY, ALL EXPRESS OR IMPLIED WARRANTIES
INCLUDING, WITHOUT LIMITATION, ANY IMPLIED WARRANTY OF MERCHANTABILITY,
FITNESS FOR A PARTICULAR PURPOSE AND NON-INFRINGEMENT ARE EXPRESSLY
DISCLAIMED BY YOU TO US AND BY US TO YOU. TO THE EXTENT THAT ANY SUCH
WARRANTIES CANNOT BE DISCLAIMED, SUCH WARRANTY IS LIMITED IN DURATION
TO THE MINIMUM PERIOD PERMITTED BY LAW.

\section{Consequential Damage Waiver}

TO THE MAXIMUM EXTENT PERMITTED BY APPLICABLE LAW, IN NO EVENT WILL
YOU OR US BE LIABLE FOR ANY LOSS OF PROFITS, LOSS OF ANTICIPATED SAVINGS,
LOSS OF DATA, INDIRECT, SPECIAL, INCIDENTAL, CONSEQUENTIAL AND EXEMPLARY
DAMAGES ARISING OUT OF THIS AGREEMENT REGARDLESS OF THE LEGAL OR
EQUITABLE THEORY (CONTRACT, TORT OR OTHERWISE) UPON WHICH THE CLAIM IS
BASED.


\section{Miscellaneous}

\subsection{}

This Agreement will be governed by and construed in accordance with the laws of
Austria excluding its conflicts of law provisions. Under certain circumstances,
the governing law in this section might be superseded by the United Nations
Convention on Contracts for the International Sale of Goods (``UN Convention'')
and the parties intend to avoid the application of the UN Convention to this
Agreement and, thus, exclude the application of the UN Convention in its
entirety to this Agreement.

\subsection{}

This Agreement sets out the entire agreement between You and Us for Your
Contributions to Us and overrides all other agreements or understandings.

\subsection{}

If You or We assign the rights or obligations received through this Agreement to
a third party, as a condition of the assignment, that third party must agree in
writing to abide by all the rights and obligations in the Agreement.

\subsection{}

The failure of either party to require performance by the other party of any
provision of this Agreement in one situation shall not affect the right of a
party to require such performance at any time in the future. A waiver of
performance under a provision in one situation shall not be considered a waiver
of the performance of the provision in the future or a waiver of the provision
in its entirety.

\subsection{}

If any provision of this Agreement is found void and unenforceable, such
provision will be replaced to the extent possible with a provision that comes
closest to the meaning of the original provision and which is enforceable. The
terms and conditions set forth in this Agreement shall apply notwithstanding any
failure of essential purpose of this Agreement or any limited remedy to the
maximum extent possible under law.\\

\vspace{1.5cm}
\noindent\textbf{You}\\
Date: \rule{0.2\textwidth}{0.5pt} Signature: \hrulefill \\\\
Name: \hrulefill\\\\
Title: \hrulefill\\\\
Address: \hrulefill\\
\hrulefill\\

\vspace{1cm}
\noindent\textbf{Us}\\
The \texttt{ViennaRNA Package} Core Development Team\\
Ivo L. Hofacker \& Ronny Lorenz\\
Institute for Theoretical Chemistry - University of Vienna\\
W{\"a}hringer Stra{\ss}e 17\\
1090 Vienna - AUSTRIA


\end{document}
